Fivebranes

### 2022-05-26 fivebranes/kr.tex
unrefined

Given this description, there is a simple expression for the character 
\[
\ch\, {M(F(\lambda_1,\lambda_2;\lambda_3;y))} = q^{-y} t_1^{\lambda_1}t_2^{\lambda_2} r^{\lambda_3} R(q,t_1,t_2,r) \cdot {\rm sdim}( V )
\]
where $R = \ch \Sym(\fg_{<0})$.

@@

\parsec[s:typeA]

There is a cohomological description of the irreducible modules of type $A$
\[
I(p,0;r;\frac23 p - r) .
\]
In \cite{KR2}, an exact sequence of $E(3|6)$-modules is constructed
\[
0 \leftarrow I(p,0;r;\frac23 p - r) \leftarrow M(p, 0 ; r;\frac23 p - r) \leftarrow M(p+1, 0;r+1;\frac23 p - r - \frac13) \leftarrow \cdots 
\]
which is
\[
0 \leftarrow I(p,0;r;\frac23 p - r) \leftarrow M(V^{p,r}) \leftarrow M(V^{p+1,r+1}) \leftarrow \cdots .
\]

84rPqzleGThz

>>>>

Given this description, there is a simple expression for the character 
\[
\ch\, {M(F(\lambda_1,\lambda_2;\lambda_3;y))} = q^{-\frac32 y} t_1^{\lambda_1}t_2^{\lambda_2} r^{\lambda_3} R(q,t_1,t_2,r) \cdot {\rm sdim}( V )
\]
where $R = \ch \Sym(\fg_{<0})$.

@@

For notational simplicity, we will set $q = t^2$.

\subsection{Characters for degenerate modules of type A} \label{s:typeA}

There is a cohomological description of the irreducible modules of type $A$
\[
I(\lambda_1,0,\lambda_3;\frac23 \lambda_1 - \lambda_3) .
\]
In \cite{KR2}, an exact sequence of $E(3|6)$-modules is constructed
\beqn\label{eqn:les1}
0 \leftarrow I(\lambda_1,0,\lambda_3;\frac23 \lambda_1 - \lambda_3) \leftarrow M(\lambda_1,0,\lambda_3;\frac23 \lambda_1 - \lambda_3) \leftarrow M(\lambda_1+1,0,\lambda_3+1;\frac23 \lambda_1 - \lambda_3-\frac13) \leftarrow \cdots .
\eeqn
%which is
%\[
%0 \leftarrow I(p,0;r;\frac23 p - r) \leftarrow M(V^{p,r}) \leftarrow M(V^{p+1,r+1}) \leftarrow \cdots .
%\]

\parsec[s:typeAunrefinedKR]
In this section we compute the {\em unrefined} character of the type A modules $I_A(\lambda_1,\lambda_3)$ where we specialize $t_1=t_2=1$.
From the long exact sequence \eqref{eqn:les1} we have the following expression 
\[
\ch I_A(\lambda_1,\lambda_3)|_{t_1=t_2=1} = \sum_{j \geq 0} \ch M(\lambda_1+j,0,\lambda_3+j;\frac23 \lambda_1 - \lambda_3 - \frac{j}{3}) .
\]

Let $M_j$ be the $j$th Verma module appearing in the sum above. 
Then
\beqn
\ch M_j = R(r,t) t^{3 \lambda_3 - 2 \lambda_1} \frac{(\lambda_1+j+1)(\lambda_1+j+2)}{2} t^j \left(r^{\lambda_3+j}+ r^{\lambda_3+j-2} + \cdots + r^{-\lambda_3-j} \right) .
\eeqn
Notice that 
\[
r^{\lambda_3+j}+ r^{\lambda_3+j-2} + \cdots + r^{-\lambda_3-j} = \frac{r^{\lambda_3+j}-r^{-\lambda_3-j-2}}{1-r^{-2}} ,
\]
so the above expression for $\ch M_j$ reduces to
\[
\ch M_j = R(r,t) t^{3 \lambda_3 - 2 \lambda_1} \frac{(\lambda_1+j+1)(\lambda_1+j+2)}{2} \frac{r^{\lambda_3+j}-r^{-\lambda_3-j-2}}{1-r^{-2}} t^j .
\]
Observe the formal identity 
\[
\sum_{j \geq 0} \frac{(\lambda_1+j+1)(\lambda_1+j+2)}{2} x^j = \frac{p(x)}{(1-x)^3}  .
\]
where $p(x) = \frac12 \left(\lambda_1^2 x^2 + \lambda_1 x^2 - 2\lambda_1^2x -4 \lambda_1 x + \lambda_1^2 + 3\lambda_1 +2\right)$.

Using this identity, we evaluate
\begin{align*}
\ch I_A(\lambda_1,\lambda_3) & = \frac{R(r,t) t^{3 \lambda_3 - 2 \lambda_1}}{1-r^{-2}} \left(\frac{r^{\lambda_3} p(tr)}{(1-tr)^3} - \frac{r^{-\lambda_3-2}p(tr^{-1})}{(1-tr^{-1})^3} \right) \\ 
& = \frac{t^{3 \lambda_3-2\lambda_1}}{(1-t^2)^3(1-r^{-2})} \left(r^{\lambda_3} p(tr) (1-tr^{-1})^3 - r^{-\lambda_3-2} p(tr^{-1})(1-tr)^3 \right) .
\end{align*}

Finally, we specialize further $t=r$ and substitute $q = t^2$ to obtain
\[
\ch I_A(\lambda_1,\lambda_3) = \frac{q^{\lambda_3 - \lambda_1}}{1-q} .
\]

\subsection{Characters for degenerate modules of type B} \label{s:typeB}

There is a cohomological description of the irreducible modules of type $B$ similar to the type A case above.
Let $I_B(\lambda_1,\lambda_3) = I(\lambda_1,0,\lambda_3;\frac23 \lambda_1 - \lambda_3+2)$. 
We are only interested in the case $\lambda_1 = 0$.  
In \cite{KR2}, an exact sequence of $E(3|6)$-modules is constructed
\begin{multline}\label{eqn:les1}
0 \leftarrow  I_B(0,\lambda_3) \leftarrow \\ \leftarrow M(0,0,\lambda_3;\lambda_3 + 2) \leftarrow  M(1,0,\lambda_3-1;\frac{11}{3} - \lambda_3)  \leftarrow \cdots \leftarrow M(\lambda_3, 0, 0;\frac23 \lambda_3 +2) \leftarrow \\
 \leftarrow M(\lambda_3+2, 0, 0; \frac23 \lambda_3 + \frac43) \leftarrow M(\lambda_3+3, 0, 1; \frac23 \lambda_3 + 2) \leftarrow \cdots .
\end{multline}
There are $\lambda_3+1$ terms in the second line above .

\parsec[s:typeBunrefinedKR]
